Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-26 ms.tex
bg table notes

This paper is organized as follows.
In \textsection2, we develop stellar properties through
photometric and spectroscopic data.
In \textsection3, we combine the derived stellar properties with \KT\ data to infer planet
candidate properties.
In \textsection4, we combine adaptive optics and radial velocity observations with both
archival and modern ground-based, seeing limited survey data and an analysis of the
transit parameters to calculate false positive probabilities.
In \textsection5, we discuss potentially interesting systems.
In \textsection6, we summarize and discuss our results.

@@

As has been well known from the early days of transit searches, it is
possible for an eclipsing binary star to masquerade as a transiting
planet. 
There are many scenarios which can cause an astrophysical false positive.
The most common scenarios are if (a) it is a highly grazing eclipse, or (b) the binary system
shares a photometric aperture with a significantly brighter star, 
resulting in a diluted eclipse depth.
When possible, such astrophsycial false positive scenarios are traditionally
ruled out by detailed follow-up observations, often a combination of
high-resolution imaging and radial-velocity measurements.
However, the \kep\ mission, with its thousands of planet candidates
around mostly faint stars, necessitated a paradigm shift---a move
toward probabilistic interpretation of transit signals, rather than
comprehensive follow-up of each individual candidate \citep{Morton11b}.

@@

To investigate the possibility that such wide companions exist,
we query the ninth data release of the Sloan Digital Sky Survey
\citep[SDSS DR9,][]{Ahn12}.
For each target, we return
all stars within 12\arcsec\ with $\Delta r < 8$ relative to each object
of interest.
Of the 31 stars in our sample, four have such a companion.
Unlike the original \kep\ field, the field for \KT\ \Ci\ is
well out of the galactic plane, so the rate of giant, distant background
stars is significantly lower.
We include all potential contaminants in Table 5.

@@

SDSS is 95\% complete at $r=22.2$ and the telescope has a point
spread function of $1\farcs4$. In all cases except the four above, we
treat the SDSS data as providing a contrast curve at wide separations
down to a limiting magnitude of $r=22.2$.

@@

Unlike GJ\,1214b, EPIC 201912552b is not highly irradiated.
Instead, it is at a reduced semimajor axis \ars$ = 84.3 \pm 9.5$.
Its equilibrium temperature is then, assuming zero albedo, $T_{eq} = 271 \pm 16$
K, meaning its bulk insolation is $128 \pm 28$ percent that of the Earth's.
Although the planet is likely too large to be rocky \citep{Rogers14},
its atmosphere is likely to be the focus of many future observations, providing
a cool analogue to the highly irradiated planets of a similar size found by
\kep.

>>>>

This paper is organized as follows.
In \textsection2, we develop stellar properties through
photometric and spectroscopic data.
In \textsection3, we combine the derived stellar properties with \KT\ data to infer planet
candidate properties.
In \textsection4, we combine adaptive optics and radial velocity observations with both
archival and modern ground-based, seeing limited survey data and an analysis of the
transit parameters to calculate false positive probabilities.
In \textsection5, we discuss potentially interesting systems, including a mini-Neptune
orbiting an M dwarf which receives a similar insolation to the Earth.
In \textsection6, we summarize and discuss our results.

@@

There are many scenarios which can cause an astrophysical false positive,
where an eclipsing binary star masquerades as a transiting planet.
The most common scenarios are if (a) it is a highly grazing eclipse, or (b) the binary system
shares a photometric aperture with a significantly brighter star, 
resulting in a diluted eclipse depth.
When possible, such astrophyscial false positive scenarios are traditionally
ruled out by detailed follow-up observations, often a combination of
high-resolution imaging and radial-velocity measurements.
However, the \kep\ mission, with its thousands of planet candidates
around mostly faint stars, necessitated a paradigm shift---a move
toward probabilistic interpretation of transit signals, rather than
comprehensive follow-up of each individual candidate \citep{Morton11b}.

@@

To investigate the possibility that such wide companions exist,
we query the ninth data release of the Sloan Digital Sky Survey
\citep[SDSS DR9,][]{Ahn12}.
For each target, from the depth of the observed transit we determine how
bright a background object must be to cause the event if the background
object were an equal mass totally-eclipsing binary.
We then search for all stars within 25\arcsec\ that are within this brightness
limit relative to the candidate host star.
All apertures we use in our \KT\ analysis are smaller than 20\arcsec\ so this
search should encompass the region where possible background 
contaminants could reside.
Of the 31 stars in our sample, eleven have such a companion.

Unlike the original \kep\ field, the field for \KT\ \Ci\ is
well out of the galactic plane, so the rate of giant, distant background
stars is significantly lower.
We include all potential contaminants in Table 5.
We validate or eliminate each of these as a possibility based on the transit shape.
For example, the events near EPIC 201546283 could only be caused by a 
background binary if the background object was a completely-eclipsing system
(so that the eclipse depth was $50\%$). 
In this case, the transit would be perfectly V-shaped.
Since it is not, we can rule out the possibility this background object causes
the transit event.

@@

SDSS is 95\% complete at $r=22.2$ mag and the telescope has a point
spread function of $1\farcs4$. In all cases except the four above, we
treat the SDSS data as providing a contrast curve at wide separations
down to a limiting magnitude of $r=22.2$ mag.

@@

The planet is slightly smaller than GJ\,1214b, but unlike that planet,
EPIC 201912552b is not highly irradiated.
Instead, it is at a reduced semimajor axis \ars$ = 84.3 \pm 9.5$.
Its equilibrium temperature is then, assuming zero albedo, $T_{eq} = 271 \pm 16$
K, meaning its bulk insolation is $128 \pm 28$ percent that of the Earth's.
Although the planet is likely too large to be rocky \citep{Rogers14},
its atmosphere is likely to be the focus of many future observations, providing
a cool analogue to the highly irradiated planets of a similar size found by
\kep.
